Amicus Structure

### 2021-11-04 eda/amicus-structure.Rmd
reorg

```{r}
amicus_summary %>% filter(case == "Harris v. McRae", !summary)
```

>>>>

```{r}
amicus_summary %>% filter(!summary) %>% group_by(intro, statement) %>% summarize(n=n())
```

```{r}
amicus_summary %>% filter(grepl("docx", brief), !summary)
```

```{r}
sum_id <- readxl::read_excel(path = "../reference_files/docx_summary_ids.xlsx")
sum_id %>% head(5)
```

```{r}
amicus %>% filter(id == 861820896073) %>% 
  mutate(t = grepl("protecting a woman’s health. argument", txt_full)) %>% 
  select(t)
```
